General Discussion

### 2024-04-06 Sections/Appendix/E1_Appendix.qmd
render full in pdf and markdown

```{r}
# print(getwd())
# here::set_here(path='..')
# print(getwd())
source(here::here("Functions", "packages.R"))

>>>>

```{r}
# print(getwd())
# here::set_here(path='..')
# print(getwd())
#source(here::here("Functions", "packages.R"))
pacman::p_load(dplyr,purrr,tidyr,tibble,ggplot2,
  brms,tidybayes, rstanarm,emmeans,broom,bayestestR,
  stringr, here,conflicted, patchwork, knitr, cowplot, RColorBrewer,data.table,gt,
  ggh4x,htmltools,future,furrr,ez)

### 2024-04-06 Sections/Discussion.qmd
render full in pdf and markdown

---
title: General Discussion
date: today
---

@@

>>>>

---
title: General Discussion
date: today
format:
  html: default
  hugo-md:
    #echo: false
    #output: false
    html-math-method: mathjax
    output-file: dissc_hugo.md
    mermaid-format: png
  gfm:
    #echo: false
    output-file: dissc_gfm.md
    mermaid-format: png
---

@@

### test

```{r}
#| echo: false
#| include: false 
out_type <- knitr::opts_knit$get("rmarkdown.pandoc.to")
print(out_type)

fmt_out <- knitr::pandoc_to()
print(fmt_out)

out_type %in% c("html","pdf")

# out_type = "html"
out_type == "html" || out_type == "pdf" || out_type == "docx"

primary=out_type == "html" || out_type == "pdf" || out_type == "docx"

ifelse(knitr::pandoc_to() %in% c("html","pdf","docx"), TRUE, FALSE)

```

::: {.content-visible unless-format="markdown"}
```{dot}
//| label: fig-design-e1
//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
//| fig-width: 7.0
//| fig-height: 2.5
//| fig-responsive: false
//| echo: false 
///| include: !expr "html" || out_type == "pdf" || out_type == "docx"

/////| column: screen-inset-right
digraph {
  graph [layout = dot, rankdir = LR]

  // define the global styles of the nodes
  node [shape = rectangle, style = filled]

  data1 [label = " Varied Training \n800-1000\n1000-1200\n1200-1400", fillcolor = "#FF0000"]
  data2 [label = " Constant Training \n800-1000", fillcolor = "#00A08A"]
  Test3 [label = "    Final Test \n  Novel With Feedback  \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]

  // edge definitions with the node IDs
  data1 -> Test1
  data2 -> Test1

  subgraph cluster {
    label = "Test Phase \n(Counterbalanced Order)"
    Test1 [label = "Test  \nNovel Bands \n100-300\n350-550\n600-800", fillcolor = "#ECCBAE"]
    Test2 [label = "  Test \n  Varied Training Bands  \n800-1000\n1000-1200\n1200-1400", fillcolor = "#ECCBAE"]
    Test1 -> Test2
  }

  Test2 -> Test3
}
```
:::
